Supplementary material

### 2025-09-10 resubmission/07-supplementary-material.qmd
changes supplementary material

options(kableExtra.html.bsTable = T)
options(knitr.kable.NA = "")
```

@@

```{r}
#| label: fig-matrix
#| out-width: '90%'
#| fig-asp: 1
#| fig-cap: "Correlation matrix of the main variables for the last wave (2023)"
#| fig-cap-location: top
#| echo: false
#| results: asis

@@

#Plot the matrix using corrplot
corrplot::corrplot(M,
                   method = "color",
                   addCoef.col = "black",
                   type = "upper",
                   tl.col = "black",
                   col = colorRampPalette(c("#E16462", "white", "#0D0887"))(12),
                   bg = "white",
                   na.label = "-")

@@

texreg::texreg(list(m0, m1, m2, m3, m4, m5, m6, m7),
               custom.model.names = c("Model 0",paste0("Model ", seq(1:7))),
               caption = "Complete longitudinal multilevel models for market justice preferences",
               caption.above = T,
               stars = c(0.05, 0.01, 0.001),
               custom.coef.map = ccoef,
               digits = 3,
               groups = list("Wave (Ref.= 2016)" = 2:6,
                             "Income quintile (Ref.= Quintile 1)" = 16:20,
                             "Political identification (Ref.= Left)" = 22:24,
                             "Age (Ref.= 18-29)" = 26:28),
               custom.note = "Note: Cells contain regression coefficients with standard errors in parentheses. %stars.",
               leading.zero = T,
               use.packages = F,
               booktabs = F,
               scalebox = 0.5,
               include.loglik = FALSE,
               include.aic = FALSE,
               center = T,
               custom.gof.names = c("BIC", "Numb. obs.", "Num. groups: individuals", "Var: individuals (Intercept)", "Var: Residual", "Var: individuals, wave", "Cov: individuals (Intercept), wave"))

@@

texreg::texreg(list(m10.1, m11.1, m12.1, m10.2, m11.2, m12.2),
               custom.model.names = c("Model 12", "Model 13", "Model 14", "Model 15", "Model 16", "Model 17"),
               caption = NULL,
               stars = c(0.05, 0.01, 0.001),
               custom.coef.map = ccoef,
               digits = 3,
               caption.above = T,
               custom.note = "Note: Cells contain regression coefficients with standard errors in parentheses. %stars. CWC = centered within group.",
               leading.zero = T,
               use.packages = F,
               booktabs = F,
               scalebox = 0.7,
               include.loglik = FALSE,
               include.aic = FALSE,
               center = T,
               custom.gof.names = c("BIC", 
                                    "Numb. obs.", 
                                    "Num. groups: individuals", 
                                    "Var: individuals (Intercept)",

@@

texreg::texreg(list(m15.1, m16.1, m17.1, m15.2, m16.2, m17.2),
               custom.model.names = c("Model 18", "Model 19", "Model 20", "Model 21", "Model 22", "Model 23"),
               caption = NULL,
               stars = c(0.05, 0.01, 0.001),
               custom.coef.map = ccoef,
               digits = 3,
               caption.above = T,
               custom.note = "Note: Cells contain regression coefficients with standard errors in parentheses. %stars. CWC = centered within group.",
               leading.zero = T,
               use.packages = F,
               booktabs = F,
               scalebox = 0.5,
               include.loglik = FALSE,
               include.aic = FALSE,
               center = T,
               custom.gof.rows = list("Controls"=c(rep("Yes",6))))

>>>>

options(kableExtra.html.bsTable = T)
options(knitr.kable.NA = "")

@@

```{r}
#| label: fig-matrix
#| out-width: '90%'
#| fig-asp: 1
#| fig-cap: "Correlation matrix of the main variables for the first wave (2016)"
#| fig-cap-location: top
#| echo: false
#| results: asis

@@

#Plot the matrix using corrplot
corrplot::corrplot(M,
                   method = "color",
                   addCoef.col = "black",
                   type = "upper",
                   tl.col = "black",
                   col = colorRampPalette(c("#E16462", "white", "#0D0887"))(12),
                   bg = "white",
                   na.label = "-") 
grid::grid.text("Source: own elaboration with data from ELSOC 2016 (n = 1687)", x = 0.99, y = 0.1, just = "right", gp = grid::gpar(fontsize = 12, col = "black"))

@@

texreg::texreg(list(m0, m1, m2, m3, m4, m5, m6, m7),
               custom.model.names = c("Model 0",paste0("Model ", seq(1:7))),
               caption = "Complete longitudinal multilevel models for market justice preferences",
               caption.above = T,
               stars = c(0.05, 0.01, 0.001),
               custom.coef.map = ccoef,
               digits = 3,
               groups = list("Wave (Ref.= 2016)" = 2:6,
                             "Income quintile (Ref.= Quintile 1)" = 16:20,
                             "Political identification (Ref.= Left)" = 22:24,
                             "Age (Ref.= 18-29)" = 26:28),
               custom.note = "Note: Cells contain regression coefficients with standard errors in parentheses. %stars.
Source: own elaboration with pooled data from ELSOC 2016-2023 (N obs = 8643; N groups = 1687)",
               leading.zero = T,
               use.packages = F,
               booktabs = F,
               scalebox = 0.5,
               include.loglik = FALSE,
               include.aic = FALSE,
               center = T,
               custom.gof.names = c("BIC", "Numb. obs.", "Num. groups: individuals", "Var: individuals (Intercept)", "Var: Residual", "Var: individuals, wave", "Cov: individuals (Intercept), wave"))

@@

texreg::texreg(list(m10.1, m11.1, m12.1, m10.2, m11.2, m12.2),
               custom.model.names = c("Model 12", "Model 13", "Model 14", "Model 15", "Model 16", "Model 17"),
               caption = NULL,
               stars = c(0.05, 0.01, 0.001),
               custom.coef.map = ccoef,
               digits = 3,
               caption.above = T,
               custom.note = "Note: Cells contain regression coefficients with standard errors in parentheses. %stars. CWC = centered within group.
Source: own elaboration with pooled data from ELSOC 2016-2023 (N obs = 8643; N groups = 1687)",
               leading.zero = T,
               use.packages = F,
               booktabs = F,
               scalebox = 0.7,
               include.loglik = FALSE,
               include.aic = FALSE,
               center = T,
               custom.gof.names = c("BIC", 
                                    "Numb. obs.", 
                                    "Num. groups: individuals", 
                                    "Var: individuals (Intercept)",

@@

texreg::texreg(list(m15.1, m16.1, m17.1, m15.2, m16.2, m17.2),
               custom.model.names = c("Model 18", "Model 19", "Model 20", "Model 21", "Model 22", "Model 23"),
               caption = NULL,
               stars = c(0.05, 0.01, 0.001),
               custom.coef.map = ccoef,
               digits = 3,
               caption.above = T,
               custom.note = "Note: Cells contain regression coefficients with standard errors in parentheses. %stars. CWC = centered within group.
Source: own elaboration with pooled data from ELSOC 2016-2023 (N obs = 8643; N groups = 1687)",
               leading.zero = T,
               use.packages = F,
               booktabs = F,
               scalebox = 0.5,
               include.loglik = FALSE,
               include.aic = FALSE,
               center = T,
               custom.gof.rows = list("Controls"=c(rep("Yes",6))))
